Constraining Supermassive Black Hole Environments.

### 2014-08-04 ms.tex
Some comments on Mdot.

\subsection{Comparison with Bondi Accretion}
The Bondi accretion rate, $\dotMb$ is given by

@@

Thus, $\cs(rs)\simeq \vw(\rs)$. This means that $\dot{M}$ in our model is quite close to \Mdotb

@@

\subsection{Mass accretion rate}
For each of our solutions, we may calculate the accretion rate $\dot{M}$ onto the SMBH. We show $\Medd$ vs. $\Mbh$ as a function of black hole mass for our three  chosen values of the $\vwO$ (200 km/s, 500 km/s, and 1000 km/s). The results are shown in Figure~\ref{fig:mdot_mass}. 
%%AG-Also want to go into the case of no stagnation radius

>>>>

\subsection{Comparison with Bondi Accretion}
The Bondi accretion rate, $\Mdotb$ is given by

@@

Thus, $\cs(rs)\simeq \vw(\rs)$. This means that $\dot{M}$ in our model is quite close to $\Mdotb$

@@

\subsection{Mass accretion rate}
For each of our solutions, we may calculate the accretion rate $\dot{M}$ onto the SMBH. We show $\Medd$ vs. $\Mbh$ as a function of black hole mass for our three  chosen values of the $\vwO$ (200 km/s, 500 km/s, and 1000 km/s). The results are shown in Figure~\ref{fig:mdot_mass}.  Note that $\dot{M}\sim\vwO^{-2}$ for a cusp galaxy and $\dot{M}\sim\vwO^{-4}$ for a core galaxy. Thus, the mass accretion rate will be a sensitive function of the assumed heating rate.
%%AG-Core galaxies might be a better choice to show the variations in the mass accretion rate 
%%AG-Also want to go into the case of no stagnation radius
